% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}

% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
        \begin{center}
        \vspace*{1.0cm}

        \Huge
        {\bf Data-Driven Models: An Alternative Discrete Hedging Strategy }

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Ke Nian \\

        \vspace*{3.0cm}

        \normalsize
        A thesis \\
        presented to the University of Waterloo \\
        in fulfillment of the \\
        thesis requirement for the degree of \\
        Doctor of Philosophy \\
        in \\
        Computer Science \\

        \vspace*{2.0cm}

        Waterloo, Ontario, Canada, 2023 \\

        \vspace*{1.0cm}

        \copyright\ Ke Nian 2023 \\
        \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.


% E X A M I N I N G   C O M M I T T E E (Required for Ph.D. theses only)
% Remove or comment out the lines below to remove this page
\begin{center}\textbf{Examining Committee Membership}\end{center}
  \noindent
The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.
  \bigskip

  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
External Examiner: \>  Kenneth R. Jackson \\
\> Professor, Computer Science Department, University of Toronto \\
\end{tabbing}
  \bigskip

  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Supervisor(s): \> Yuying Li \\
\> Professor, School of Computer Science, University of Waterloo \\
\end{tabbing}
  \bigskip

  \noindent
  \begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal Examiner: \>  Justin W.L. Wan \\
\> Professor, School of Computer Science, University of Waterloo \\
\end{tabbing}
  \bigskip


  \begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal Examiner: \>  Yaoliang Yu \\
\> Associate Professor, School of Computer Science, University of Waterloo \\
\end{tabbing}
  \bigskip
  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal-External Member: \> Tony Wirjanto \\
\> Professor, Department of Statistics and Actuarial Science, University of Waterloo \\
\end{tabbing}
  \bigskip

%  \noindent
%\begin{tabbing}
%Internal-External Member: \=  \kill % using longest text to define tab length
%Other Member(s): \> Leeping Fang \\
%\> Professor, Dept. of Fine Art, University of Waterloo \\
%\end{tabbing}

\cleardoublepage

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
  \noindent
I hereby declare that I am the sole author of this thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.

  \bigskip

  \noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage

% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}
Options hedging is a critical problem in financial risk management. The prevailing approach in financial derivative pricing and hedging has been to firstly assume a parametric model describing the underlying price dynamics.  An option model function $V$ is then calibrated to current  market option prices and various sensitivities are computed and  used to hedge the option risk.  It has been recognized that computing hedging position from the sensitivity of the calibrated model option value function is inadequate in minimizing  the variance of the option hedging risk, as it fails to capture the model parameter dependence on the underlying price.
% In this thesis, we demonstrate that this issue can exist generally when determining hedging position from the sensitivity of the option function, either  calibrated from a parametric model from spot market option prices or estimated nonparametricaly from historical option prices. Consequently the sensitivity of the estimated model option function typically does not minimize variance of the hedge risk, even instantaneously, unless the parameters dependence is addressed. 
We propose several data-driven approaches to directly learn a hedging function from the historical market option and underlying data by minimizing certain measure of the local hedging risk and total hedging risk. This thesis will focus on answering the following questions: 1) Can we efficiently build direct data-driven models for discrete hedging problem that outperform existing state-of-art parametric hedging models based on the market prices? 2) Can we incorporate feature selection and feature extraction into the data-driven models to further improve the performance of the discrete hedging? 3) Can we build efficient models for both the one-step local risk hedging problem and multi-steps total risk hedging problem based on the state-of-art learning framework such as deep learning framework and kernel learning framework?

Using the S\&P 500 index daily option data for more than a decade ending in August 2015, we firstly propose a direct data-driven approach \citep{knian2017} based on kernel learning framework and we demonstrate  that the proposed method outperforms the parametric minimum variance hedging method proposed in \citep{hulloptimal}, as well as  minimum variance hedging corrective techniques based on stochastic volatility or local volatility models.
Furthermore, we show that the proposed approach achieves significant gain over the implied Black-Sholes delta hedging for weekly and monthly hedging.

Following the direct data-driven kernel learning approach \citep{knian2017}, we propose a robust encoder-decoder  Gated Recurrent Unit (GRU) model, $\text{GRU}_{\delta}$, for optimal discrete option hedging. The proposed $\text{GRU}_{\delta}$ utilizes the Black-Scholes model as a pre-trained model and  incorporates sequential information and feature selection.  Using the S\&P 500 index European option market data from January 2, 2004 to August 31, 2015,   we demonstrate that the weekly and monthly hedging performance of the proposed $\text{GRU}_{\delta}$ significantly surpasses that of the data-driven minimum variance (MV) method in \citep{hulloptimal}, the regularized kernel data-driven model \citep{knian2017}, and the SABR-Bartlett method \cite{hagan2017bartlett}.
In addition, the daily hedging performance of the proposed $\text{GRU}_{\delta}$ also surpasses that of MV methods in \cite{hulloptimal} based on parametric models, the kernel method \citep{knian2017} and SABR-Bartlett method \cite{hagan2017bartlett}.

Lastly, we design a multi-steps data-driven models $\modelT$ based on the $\model$  to hedge the option discretely until the expiry.  We utilize SABR model and Local Volatility Function (LVF) to augment existing market data and thus alleviate the problem of  scarcity in market option prices. The augmented market data is used to train a sufficient  total risk hedging model $\modelT$.
\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

Firstly, I would like to express my deepest thanks to my advisors: Prof.Yuying Li and Prof.Thomas. F. Coleman for the continuous support of my study and related research, for their patience, motivation, and immense knowledge. Their guidance helped me in all the time of research and writing of this thesis. I could not have imagined having  better advisors and mentors for my Ph.D study. It is sad that Prof. Coleman passed away in 2021 and he cannot see the completion of this thesis. He will be always remembered as my role model. May he rest in peace.  

Besides, I am deeply indebted to my supervisors' support and empathy during Covid-19 period when I decided to be a part-time Ph.D. student and joined the financial industry. Although the working experience delayed the thesis completion a bit, I have gained a lot of insight of the value of my work. 
 
I would like to extend my sincere thanks to
the rest of my thesis committee: Prof. Justin Wan, Dr. Yaoliang Yu, Prof.Kenneth R. Jackson and Prof.Tony Wirjanto for their insightful comments and encouragement, but also for the hard question which inspired me to widen my research from various perspectives.


I had the pleasure of working with my 
lab mates: Kai Ma, Eddie Cheung, Parsiad Azimzadeh, Aditya  Tayal, Haofan Zhang, Chufeng Hu and Chendi Ni.
I will never forget those hard working nights together in the lab office, and all the fun and chat we have had.

Last but not the least, I would be remiss in not mentioning my parents: Xuemei Wang and Fushun Nian and my wife: Vera Xu for their support all along the process.  Without them, I probably would have given up on this thesis multiple times already.
\cleardoublepage

% D E D I C A T I O N
% -------------------

\begin{center}\textbf{Dedication}\end{center}

This is dedicated to the one I love. This thesis is also dedicated to my future child. We are looking forward for you to join our family some day in the future.
\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page



\listofalgorithms
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page
% GLOSSARIES (Lists of definitions, abbreviations, symbols, etc. provided by the glossaries-extra package)
% -----------------------------
\printglossaries
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

